---
title: "Fit ScoradPred to data"
author: "Guillem Hurault"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
params:
  a0: 0.04
  independent_items: FALSE
  include_calibration: TRUE
  include_treatment: TRUE
  include_trend: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      fig.height = 5,
                      fig.width = 8,
                      dpi = 200)

set.seed(2021) # Reproducibility (Stan use a different seed)

source(here::here("analysis", "00_init.R")) # Load libraries, variables and functions

score <- "SCORAD"
dataset <- "PFDC"

model <- ScoradPred(independent_items = params$independent_items,
                    a0 = params$a0,
                    include_trend = params$include_trend,
                    include_calibration = params$include_calibration,
                    include_treatment = params$include_treatment,
                    treatment_names = c("localTreatment", "emollientCream"),
                    include_recommendations = FALSE)

param <- list_parameters(model)
param2 <- list_parameters(model, full_names = TRUE)

```

```{r load-data, include=FALSE}
# NB: atm copy-pasted from `run_fit.R` because we need `df`, `scorad` and especially `id` (when dealing with treatment)

l <- load_PFDC()

POSCORAD <- l$POSCORAD %>%
  rename(Time = Day)
df <- POSCORAD %>%
  select(one_of("Patient", "Time", model$item_spec$Label)) %>%
  pivot_longer(cols = all_of(model$item_spec$Label), names_to = "Label", values_to = "Score") %>%
  drop_na()  %>%
  left_join(model$item_spec[, c("Label", "ItemID")], by = c("Label"))

# Prepare SCORAD calibration data
if (model$include_calibration) {
  cal <- scorad <- l$SCORAD %>%
    rename(Time = Day) %>%
    select(one_of("Patient", "Time", model$item_spec$Label)) %>%
    pivot_longer(cols = all_of(model$item_spec$Label), names_to = "Label", values_to = "Score") %>%
    drop_na()  %>%
    left_join(model$item_spec[, c("Label", "ItemID")], by = c("Label")) 
} else {
  cal <- NULL
}

# Prepare treatment data
treatment_lbl <- paste0(model$treatment_names, "WithinThePast2Days")
if (model$include_treatment) {
  treat <- POSCORAD %>%
    select(all_of(c("Patient", "Time", treatment_lbl))) %>%
    pivot_longer(cols = all_of(treatment_lbl), names_to = "Treatment", values_to = "UsageWithinThePast2Days") %>%
    mutate(Treatment = vapply(Treatment, function(x) {which(x == treatment_lbl)}, numeric(1)) %>% as.numeric()) %>%
    drop_na()
} else {
  treat <- NULL
}

# NB: assume no recommendation (at least outside time-series)

pt <- unique(df[["Patient"]])

id <- get_index(bind_rows(df, cal, treat))
df <- left_join(df, id, by = c("Patient", "Time"))
```

```{r load-results, include=FALSE}
file_dict <- get_results_files(outcome = score,
                               model = model$name,
                               dataset = dataset,
                               root_dir = here())
file_dict$PriorPar <- get_results_files(outcome = score,
                                        model = "ScoradPred+corr",
                                        dataset = dataset,
                                        root_dir = here())$PriorPar

fit <- readRDS(file_dict$Fit)
par <- readRDS(file_dict$FitPar)
par0 <- readRDS(file_dict$PriorPar)
```

# Model specifications: `r model$name`

- Random walk `r if (params$include_trend) {"**with trend**"}` latent dynamic
- `r ifelse(params$independent_items, "**No correlation**", "**Correlation**")` between intensity items
`r if (params$include_calibration) {"- Calibration with SCORAD measurements"}`
`r if (params$include_treatment) {"- Using treatment data"}`

# Diagnostics

```{r stan-diagnostics}
check_hmc_diagnostics(fit)

par %>%
  select(Rhat) %>%
  drop_na() %>%
  summarise(max(Rhat),
            all(Rhat < 1.1))

lapply(1, # :model$D,
       function(d) {
         pairs(fit, pars = paste0(c("sigma_meas", "sigma_lat", "rho2", "sigma_tot", "mu_y0", "sigma_y0"), "[", d, "]"))
       })
plot(fit, pars = param2$Population[1], plotfun = "trace")
# print(fit, pars = param$Population)
```

# Posterior estimates

## Sensitivity to prior

```{r prior-posterior}
HuraultMisc::plot_prior_influence(par0, par, pars = c(param2$Population, param2$Patient)) +
  # coord_cartesian(xlim = c(-1, 1)) +
  theme(legend.position = "none")
```

## Measurement vs latent noise

```{r estimates-dyn1-std, message=FALSE}
plot_grid(
  plot(fit, pars = "sigma_reltot") +
    coord_cartesian(xlim = c(0, .25)) +
    labs(title = "Normalised total standard deviation"),
  plot(fit, pars = "rho2") +
    coord_cartesian(xlim = c(0, 1)) +
    labs(title = "Relative importance of measurement variance to total variance"),
  nrow = 1)
```

```{r estimates-dyn2-std}
tmp <- lapply(c("sigma_lat", "sigma_meas"),
       function(x) {
         
         smp <- rstan::extract(fit, pars = x)[[1]]
         
         out <- model$item_spec %>%
           mutate(Variable = x,
                  Samples = lapply(1:nrow(.), function(i) {smp[, i]}),
                  Samples = map2(Samples, M, ~(.x / .y)),
                  Mean = map(Samples, mean) %>% unlist(),
                  Lower = map(Samples, ~quantile(.x, probs = .05)) %>% unlist(),
                  Upper = map(Samples, ~quantile(.x, probs = .95)) %>% unlist()) %>%
           select(-Samples)
         
         return(out)
         
       }) %>%
  bind_rows()

tmp %>%
  mutate(Variable = recode(Variable,
                           "sigma_lat" = "Latent dynamic",
                           "sigma_meas" = "Measurement"),
         Component = gsub(" ", "\n", Component)) %>%
  ggplot(aes(x = Name, y = Mean, ymin = Lower, ymax = Upper, colour = Variable)) +
  facet_grid(rows = vars(Component), scales = "free", space = "free") +
  geom_pointrange(position = position_dodge(width = .5)) +
  coord_flip(ylim = c(0, .25)) +
  scale_colour_manual(values = HuraultMisc::cbbPalette) +
  labs(x = "", y = "Estimate (normalised)", colour = "Standard deviation:") +
  theme(legend.position = "top")
# ggsave(here("results", "dynamics_std.jpg"), width = 13, height = 8, units = "cm", dpi = 300, scale = 2)
```

## Measurement distribution cut-offs

```{r estimates-cutoffs}
plot(fit, pars = "ct1") + labs(title = "Cut-offs for extent, itching and sleep")
plot(fit, pars = "ct2") + labs(title = "Cut-offs for intensity signs")
plot(fit, pars = "delta1") + labs(title = "Normalised difference between cut-offs for extent, itching and sleep")
```


## Expected correlation matrices

- Correlation of latent initial condition
- Correlation of changes in latent scores

```{r estimates-correlation, results='asis'}
if (!model$independent_items) {
    # Correlation matrix (expected value)
  
    lapply(c("Omega0", "Omega"),
           function(x) {
             omg <- rstan::extract(fit, pars = x)[[1]]
             
             tmp <- list(Mean = apply(omg, c(2, 3), mean),
                         SD = apply(omg, c(2, 3), sd),
                         Lower = apply(omg, c(2, 3), function(x) {quantile(x, probs = .05)}),
                         Upper = apply(omg, c(2, 3), function(x) {quantile(x, probs = .95)}),
                         pval = apply(omg, c(2, 3), function(x) {empirical_pval(x, 0)}))
             tmp <- lapply(tmp,
                           function(x) {
                             colnames(x) <- model$item_spec$Name
                             rownames(x) <- model$item_spec$Name
                             return(x)
             })
             
             corrplot::corrplot.mixed(tmp$Mean, lower = "number", upper = "ellipse", p.mat = tmp$pval, sig.level = 0.1)

             # corrplot::corrplot(tmp$Mean, method = "ellipse") %>%
             #   corrplot::corrRect(name = c("extent", "itching", "dryness", "thickening"))
             
             NULL
           })
  }
```

## Calibration

### Estimates

- `bias0` corresponds to the initial bias.
The value is reported as a proportion to the maximum value that the score can take.
`bias0 > 0` means that the clinician scores higher than the patient.
- `tau_bias` is the time constant associated to the learning of the patient (whether the bias is reduced with time).
  - `tau_bias >> 1` means that the patient does not learn and the bias stays constant.
  - `tau_bias << 1` means bias goes to 0 very fast

```{r estimates-calibration}
if (model$include_calibration) {
  
  # + Visualise calibration time in PPC plot
  
  p1_cal <- par %>%
    filter(Variable == "bias0") %>%
    rename(ItemID = Index) %>%
    left_join(model$item_spec, by = "ItemID") %>%
    filter(!(Name %in% c("sleep", "itching"))) %>%
    ggplot(aes(x = Name, y = Mean, ymin = `5%`, ymax = `95%`)) +
    facet_grid(rows = vars(Component), scales = "free", space = "free") +
    geom_pointrange() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    coord_flip() +
    scale_y_continuous(limits = c(-.5, .5)) +
    labs(x = "",
         y = "Initial bias (normalised)")
  p2_cal <- par %>%
    filter(Variable == "tau_bias") %>%
    rename(ItemID = Index) %>%
    left_join(model$item_spec, by = "ItemID") %>%
    filter(!(Name %in% c("sleep", "itching"))) %>%
    ggplot(aes(x = Name, y = Mean, ymin = `5%`, ymax = `95%`)) +
    facet_grid(rows = vars(Component), scales = "free", space = "free") +
    geom_pointrange() +
    scale_y_log10(breaks = 10^(0:3)) +
    coord_flip() +
    labs(x = "", y = "Characteristic learning time")
  
  if (FALSE) {
    ggsave(filename = here("results", "calibration_learningtime.jpg"),
         plot = p2_cal,
         width = 13, height = 8, units = "cm", dpi = 300, scale = 2)
  }

  plot_grid(p1_cal,
            p2_cal +
              theme(axis.text.y = element_blank(),
                    axis.ticks.y = element_blank()),
            nrow = 1,
            rel_widths = c(.55, .45))
  
}
```

### Observed PO-SCORAD trajectories overlayed with a posteriori SCORAD trajectories

A posteriori SCORAD (that the clinician would have scored) tends to be higher than the observed PO-SCORAD.
However, the bias is not constant over time as the breakdown of SCORAD may change and learning may happen.

NB: the width of the posterior distribution of SCORAD follows the assumption that SCORAD measurements std is half as much as PO-SCORAD measurements std.

```{r calibration-trajectories}
if (model$include_calibration) {
  
  aggcal <- rstan::extract(fit, pars = "agg_cal_rep")[[1]]
  aggcal <- aggcal[, , 4] # SCORAD
  
  ### Plot observed PO-SCORAD and inferred SCORAD as a fanchart
  pl <- lapply(sort(sample(pt, 4)),
               function(pid) {
                 
                 tmp <- POSCORAD %>%
                   filter(Patient == pid)
                 
                 plot_post_traj_fanchart(aggcal, id = id, patient_id = pid, max_score = 103) +
                   add_broken_pointline(tmp, aes_x = "Time", aes_y = "SCORAD", colour = "Observed PO-SCORAD") +
                   scale_colour_manual(values = c("Observed PO-SCORAD" = "black")) +
                   labs(fill = "Inferred\nSCORAD\nprobabilities", colour = "", title = paste0("Patient ", pid)) +
                   theme(legend.position = "none",
                         legend.title = element_text(size = 12))
                 
               })
  
  plot_grid(get_legend(pl[[1]] + theme(legend.position = "top")),
            plot_grid(plotlist = pl, ncol = 2),
            ncol = 1, rel_heights = c(.1, .9))

}
```

## Treatment

```{r processing-treatment-estimates, include=FALSE}
if (model$include_treatment) {
  
  param_treat <- list_parameters_treatment()
  
  # Process par: Treatment usage parameters
  for (x in param_treat$Patient) {
    par <- extract_par_indexes(par, var_name = x, dim_names = c("Patient", "Treatment"))
  }
  
  # Process par: Treatment effects
  par <- extract_par_indexes(par, var_name = "ATE", dim_names = c("ItemID", "Treatment"))
  
}
```

### Daily treatment usage

#### Parameters

```{r estimates-dailytreat}
if (model$include_treatment) {
  
      # Plot patient parameters
    par %>%
      filter(Variable %in% param_treat$Patient) %>%
      mutate(Treatment = model$treatment_names[Treatment],
             Patient = factor(Patient, levels = pt)) %>%
      ggplot(aes(x = Patient, y = Mean, ymin = `5%`, ymax = `95%`, colour = Treatment)) +
      facet_grid(cols = vars(Variable)) +
      geom_pointrange(position = position_dodge(width = .5)) +
      coord_flip(ylim = c(0, 1)) +
      scale_colour_manual(values = cbbPalette[c(2, 1)]) +
      labs(y = x, colour = "") +
      theme(legend.position = "top")

    # Plot distribution of patient parameters
    lapply(param_treat$Patient,
           function(x) {
             tmp <- rstan::extract(fit, pars = x)[[1]]
             lapply(1:2,
                    function(d) {
                      PPC_group_distribution(tmp[, , d], x, nDraws = 50) +
                        coord_cartesian(xlim = c(0, 1)) +
                        labs(title = model$treatment_names[d])
                    }) %>%
               plot_grid(plotlist = ., nrow = 1)
           }) %>%
      plot_grid(plotlist = ., ncol = 1)
    
}
```

#### Average treatment usage

```{r estimates-dailytreat-avg}
if (model$include_treatment) {
  # Average treatment usage for each patient
  ptreat <- rstan::extract(fit, pars = "p_treat")[[1]]
  lapply(pt,
         function(pid) {
           data.frame(Patient = pid,
                      Treatment = model$treatment_names,
                      AverageUsage = apply(ptreat[, id %>% filter(Patient == pid) %>% pull(Index), ], 3, mean))
         }) %>%
    bind_rows() %>%
    pivot_wider(names_from = "Treatment", values_from = "AverageUsage") %>%
    ggplot(aes(x = localTreatment, y = emollientCream)) +
    geom_point() +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))
}
```

```{r estimates-dailytreat-distribution , eval=FALSE}
if (model$include_treatment) {
  # Distribution of frequency of treatment usage
  lapply(pt,
         function(pid) {
           avg_use <- apply(ptreat[, id %>% filter(Patient == pid) %>% pull(Index), ], c(1, 3), mean) %>%
             reshape2::melt(., varnames = c("Sample", "Treatment"), value.name = "AverageUsage") %>%
             mutate(Treatment = model$treatment_names[Treatment])
           ggplot(data = avg_use,
                  aes(x = AverageUsage, colour = Treatment)) +
             geom_density() +
             coord_cartesian(xlim = c(0, 1), expand = FALSE) +
             labs(colour = "") +
             theme(legend.position = "top")
         }) %>%
    plot_grid(plotlist = ., ncol = 4)
}
```

### Treatment effects

The average treatment effects is reported as a proportion of the maximum value that the score can take.
Negative values indicate that using treatment reduces severity.
For example, if ATE=-0.05 for extent (defined in [0, M=100]), it means that using treatment would reduce, on average, the severity of extent by 5 points.

NB: to be compared to the total noise `sigma_reltot`, which yields an SNR of approx. 0.2.
With a small effect size, it would be hard to detect a difference in performance or assess treatment recommendations.

```{r estimates-ATE}
if (model$include_treatment) {
      # Prob(TreatEffect < 0)
    apply(rstan::extract(fit, pars = "ATE")[[1]], c(2, 3), function(x) {mean(x < 0)})
    
    # Plot treatment effects
    par %>%
      filter(Variable == "ATE") %>%
      mutate(Treatment = model$treatment_names[Treatment]) %>%
      left_join(model$item_spec, by = "ItemID") %>%
      ggplot(aes(x = Name, y = Mean, ymin = `5%`, ymax = `95%`, colour = Treatment)) +
      facet_grid(rows = vars(Component), scale = "free", space = "free") +
      geom_pointrange(position = position_dodge(width = .5)) +
      geom_hline(yintercept = 0, linetype = "dashed") +
      coord_flip(ylim = c(-.05, .05)) +
      scale_colour_manual(values = cbbPalette[c(2, 1)]) +
      labs(x = "", y = "Treatment effect", colour = "") +
      theme(legend.position = "top")
    # plot(fit, pars = "ATE_agg")
}
```

## Trend

- `beta` is the trend smoothing factor.
If `beta=0`, the trend does not change (constant).

```{r estimates-trend1}
if (model$include_trend) {
  plot(fit, pars = "beta") + coord_cartesian(xlim = c(0, 1))
}
```

The plot shows the expected trend for four patients.

```{r estimates-trend}
if (model$include_trend) {
  
  expected_trajectory <- function(fit, par_name, id) {
    traj <- rstan::extract(fit, pars = par_name)[[1]]
    
    mean_traj <- apply(traj, c(2, 3), mean)
    mean_traj <- as.data.frame(mean_traj)
    colnames(mean_traj) <- paste0("Item_", 1:model$D)
    mean_traj <- bind_cols(id, mean_traj) %>%
      pivot_longer(cols = starts_with("Item_"), names_to = "ItemID", values_to = par_name) %>%
      mutate(ItemID = gsub("Item_", "", ItemID) %>% as.numeric())
    
    return(mean_traj)
  }
  
  mean_trend <- expected_trajectory(fit, "trend", id) %>%
    left_join(model$item_spec, by = "ItemID") %>%
    mutate(trend = trend / M)
  
  p_trend <- lapply(sort(sample(pt, 4)),
         function(pid) {
           mean_trend %>%
             filter(Patient == pid) %>%
             ggplot(aes(x = Time, y = trend, colour = Name)) +
             geom_line() +
             coord_cartesian(ylim = c(-1, 1)) +
             labs(title = paste0("Patient ", pid), colour = "") +
             theme(legend.position = "none")
         })
  
  plot_grid(get_legend(p_trend[[1]] + theme(legend.position = "top")),
            plot_grid(plotlist = p_trend, ncol = 2),
            ncol = 1, rel_heights = c(.1, .9))
}
```

```{r range-trend, message=FALSE}
if (model$include_trend) {
  
  mean_trend %>%
    group_by(Patient, Name) %>%
    summarise(Min = min(trend), Max = max(trend)) %>%
    mutate(Patient = factor(Patient)) %>%
    ggplot(aes(x = Patient, ymin = Min, ymax = Max, colour = Name)) +
    geom_errorbar(position = position_dodge(width = .7)) +
    coord_flip(ylim = c(-.01, .01)) +
    labs(y = "Range of the (normalised) expected trend", colour = "")
  # ggsave(here("results", "trend_range.jpg"), width = 13, height = 8, units = "cm", dpi = 300, scale = 2.5)
  
}
```

# Posterior predictive checks

```{r ppc, eval=FALSE}
yrep <- rstan::extract(fit, pars = "y_rep")[[1]]
aggrep <- rstan::extract(fit, pars = "agg_rep")[[1]]
df_agg <- POSCORAD %>%
  rename(Score = all_of(detail_POSCORAD(score)$Label)) %>%
  select(Patient, Time, Score) %>%
  drop_na()
pl <- lapply(pt,
             function(pid) {
               
               if (model$include_calibration) {
                 cal_time <- scorad %>% filter(Patient == pid) %>% pull(Time)
               }
               
               # Breakdown
               pl <- lapply(1:model$D,
                            function(d) {
                              tmp <- model$item_spec %>% filter(ItemID == d)
                              reso <- tmp[["Resolution"]]
                              M <- tmp[["Maximum"]] / tmp[["Resolution"]]
                              yrep_d <- yrep[, , d] * reso
                              sub_df <- df %>% filter(ItemID == d, Patient == pid)
                              if (M < 20) {
                                p <- plot_post_traj_pmf(yrep_d,
                                                        id = id,
                                                        patient_id = pid,
                                                        max_score = tmp[["Maximum"]])
                              } else {
                                p <- plot_post_traj_fanchart(yrep_d,
                                                             id = id,
                                                             patient_id = pid,
                                                             max_score = tmp[["Maximum"]],
                                                             legend_fill = "discrete",
                                                             CI_level = seq(.1, .9, .2))
                              }
                              p <- p +
                                geom_point(data = sub_df,
                                           aes(x = Time, y = Score)) +
                                geom_path(data = sub_df,
                                          aes(x = Time, y = Score)) +
                                labs(y = tmp$Label)
                              
                              if (model$include_calibration) {
                                p <- p + geom_vline(xintercept = cal_time, colour = "black")
                              }
                              
                              return(p)
                            })
               # Aggregate
               sub_df_agg <- filter(df_agg, Patient == pid)
               p_agg <- plot_post_traj_fanchart(aggrep[, , 4], # SCORAD
                                                id = id,
                                                patient_id = pid,
                                                max_score = detail_POSCORAD(score)$Maximum,
                                                legend_fill = "discrete",
                                                CI_level = seq(.1, .9, .2)) +
                 geom_point(data = sub_df_agg,
                            aes(x = Time, y = Score)) +
                 geom_path(data = sub_df_agg,
                           aes(x = Time, y = Score)) +
                 labs(y = score)
               
               if (model$include_calibration) {
                 p_agg <- p_agg + geom_vline(xintercept = cal_time, colour = "black")
               }
               
               plot_title <- ggdraw() +
                 draw_label(paste0("Patient ", pid),
                            fontface = "bold",
                            size = 20,
                            x = .5,
                            hjust = 0) +
                 theme(plot.margin = margin(0, 0, 0, 7))
               
               plot_grid(plot_title,
                         plot_grid(plotlist = pl, ncol = 1, align = "v"),
                         p_agg,
                         ncol = 1,
                         rel_heights = c(.5, 8, 2), align = "v")
             })

if (FALSE) {
  for (i in seq_along(pt)) {
    ggsave(filename = here("results", paste0(score, "_", model$name, "_", sprintf("%02d", pt[i]), ".jpg")),
           plot = pl[[i]],
           width = 10,
           height = 15,
           units = "cm",
           dpi = 300,
           scale = 3.5,
           bg = "white")
  }
}
```

```{r ppc-scorad-only, eval=FALSE}
aggrep <- rstan::extract(fit, pars = "agg_rep")[[1]]
df_agg <- POSCORAD %>%
  rename(Score = all_of(detail_POSCORAD(score)$Label)) %>%
  select(Patient, Time, Score) %>%
  drop_na()

pl <- lapply(pt,
             function(pid) {
               sub_df_agg <- filter(df_agg, Patient == pid)
               
               p_agg <- plot_post_traj_fanchart(aggrep[, , 4], # SCORAD
                                                id = id,
                                                patient_id = pid,
                                                max_score = 55,
                                                legend_fill = "discrete",
                                                CI_level = seq(.1, .9, .2)) +
                 geom_point(data = sub_df_agg,
                            aes(x = Time, y = Score)) +
                 geom_path(data = sub_df_agg,
                           aes(x = Time, y = Score)) +
                 labs(y = score, title = paste0("Patient ", pid))
             })


plot_grid(plotlist = pl[sort(sample(pt, 4))],
          ncol = 2)


if (FALSE) {
  for (i in seq_along(pt)) {
    ggsave(filename = here("results", paste0(score, "-only_", model$name, "_", sprintf("%02d", pt[i]), ".jpg")),
           plot = pl[[i]],
           width = 12,
           height = 7,
           units = "cm",
           dpi = 300,
           scale = 1.8,
           bg = "white")
  }
}

```

```{r ppc-links2, results='asis'}
img <- data.frame(Patient = pt) %>%
  mutate(File = file.path("results", paste0(score, "_", model$name, "_", sprintf("%02d", Patient), ".jpg"))) %>%
  filter(file.exists(here(File))) %>%
  mutate(Link = file.path("..", File),
         Link = gsub("\\+", "%2B", Link),
         # Link = paste0("![](", Link, ")")) %>%
         Link = paste0("- [Patient ", Patient, "](", Link, ")")) %>%
  pull(Link) %>%
  cat(sep = "\n")
# NB: printing of images does not always work, so just put the links
```

NB: the plots are not generated during the report generation but beforehand.
If nothing appears, it may be because the plots are not saved (files not found).
